---
title: "SNAP-Ed Resources"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
#library(tidyverse)
library(dplyr)
library(readr)
library(leaflet)
library(sf)
#library(shinyWidgets)
#library(rgdal)
#library(ggmap)

gacounties<-read_csv("data/county_list.csv") %>%
  arrange(fullname)

# years<-c(2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018)

```

SNAP-Ed Food Resources
=====================================  

Column {.sidebar data-width=400}
-----------------------------------------------------------------------

### Data selection

This map allows you to view SNAP and WIC authorized retailers in Georgia by. Choose the name of the county in the county selection search box and then select the relevant program. Click on a point to see more information on that retailer.

```{r input_pane}
selectInput("county","County selection",
            choices=gacounties$fullname,
            selected="Fulton County, GA")

# textInput(inputId = "address", label = "Enter address:", 
#             value="", placeholder = "e.g. 210 Field St., Athens, GA, 30602")
# actionButton("update" , label = HTML("Update map and center<br />around provided address"), icon("refresh"), class = "btn btn-primary")

checkboxGroupInput("auth_program", 
                    ("Source"), 
                    choices = list("SNAP" = "SNAP", 
                                   "WIC" = "WIC"),
                              selected = c("SNAP","WIC"))
                              
checkboxGroupInput("storegroup",
                    ("Store group"),
                    choices = list("Farmers Market" = "Farmers Market",
                                   #"Food Pantry" = "Food Pantry",
                                   "Grocery" = "Grocer",
                                   "Local Foods" = "Local foods",
                                   "Small Retail" = "Small retail",
                                   "Specialty" = "Specialty",
                                   "Supermarket" = "Supermarket",
                                   "Other Store" = "Other store",
                                   "WIC_No Category" = "WIC_No category"),
                    selected = c("Farmers Market","Grocer", "Local foods",
                         "Small retail", "Specialty", "Supermarket", "Other store", "WIC_No category"))

radioButtons("pantry_sel",
                   ("Show food pantries?"),
                   choices=list("Yes","No"))

HTML("If no stores are visible, click on the button below")

actionButton("loadstores1","Load stores")

HTML("<br>Download a spreadsheet of selected retailers<br>")

downloadButton('downloadData','Download Result Set')

downloadHandler(filename = function() {
     paste("SNAPretailers_",input$county,"_",Sys.Date(),".csv",sep="")
   },
     content = function(file) {
     write.csv(countydata_select(), file, row.names = FALSE)
   }
)

HTML("<br>Data source: USDA Benefits Redemption Division<br>")


```

Column {data-height=600}
-----------------------------------------------------------------------

```{r retail_sites}
#Load county boundary
cty_boundary<-reactive({
  st_fips<-as.character(gacounties %>%
    dplyr::filter(fullname==input$county) %>%
    mutate(fips=paste("G",stcty_fips,sep="")) %>%
    select(fips))
  
  cty_fips<-gacounties %>%
    filter(fullname==input$county) %>%
    mutate(cty_fips_sel=paste("G",stcty_fips,sep=""),
           st_fips=paste("G",st_fips,sep="")) %>%
    select(cty_fips_sel,st_fips)
  st_fips<-cty_fips$st_fips
  cty_select<-st_read("data/uscounties_st.gpkg",layer=st_fips) %>%
    filter(CTY_TXT==cty_fips$cty_fips_sel)
  # cty_boundary1<-as_Spatial(cty_select)
  # spTransform(cty_boundary1, CRS("+init=epsg:4326"))
  # cty_boundary1<-st_transform(cty_select,4326)
})

# #Load ga_retailers
# retailersdata<-reactive({
#     data<-st_read("data/program_retail_ga.GeoJSON")
#   })

#Load store data from county selection
  storedata<-st_read("data/program_retail_ga.GeoJSON",quiet=TRUE) %>%
    mutate(lat=X,long=Y,
      #Define the popup
      addr_full=if_else(is.na(addr_add),
                         paste("<br><b>",addr_num," ",addr_st," ",sep=""),
                         paste("<br><b>",addr_num," ",addr_st," ",addr_add,sep="")),
      content=paste("<strong><size=1>",store_name,"</strong></size>", 
                       addr_full,
                       "<br>",city,", ",state,"  ",zip5,"</b>",
                       "<br><b>Phone: </b>",Phone,
                       "<br><br><b>USDA store classification:</b> ",store_type,
                       "<br><b>Group category: </b>",store_grou,
                       "<br><b>Authorization: </b>",program,
                       "<br>*2018 year data are available.",sep=""))
  pantries<-storedata %>%
    filter(store_grou=="Food Pantry")
  
#Subset data based on source 
  ###NEED TO ADD BUTTON FOR PANTRIES
countydata_select<-reactive({
  grp1<-storedata %>%
    filter(sour_auth %in% input$auth_program & store_grou %in% input$storegroup) 
  
  grp2<-if(input$pantry_sel=="No"){grp1} else {rbind(grp1,pantries)}
  grp2
})

# observeEvent
# countydata_df<-reactive({
#   countydata_select()
# st_set_geometry(NULL) %>%
#   select(-lat,-long,-addr_full,-content)
# })

#Create a map  
  buffer<-0.02

output$map<-renderLeaflet({
  long_max<-as.vector(st_bbox(cty_boundary()))[3]+buffer
  latit_max<-as.vector(st_bbox(cty_boundary()))[4]+buffer
  long_min<-as.vector(st_bbox(cty_boundary()))[1]-buffer
  latit_min<-as.vector(st_bbox(cty_boundary()))[2]-buffer

  leaflet(storedata) %>%
    fitBounds(long_min,latit_min,long_max,latit_max) %>%
        addProviderTiles(providers$CartoDB.Positron) 
})

observeEvent(input$county,{
  long_max1<-as.vector(st_bbox(cty_boundary()))[3]+buffer
  latit_max1<-as.vector(st_bbox(cty_boundary()))[4]+buffer
  long_min1<-as.vector(st_bbox(cty_boundary()))[1]-buffer
  latit_min1<-as.vector(st_bbox(cty_boundary()))[2]-buffer
  
  leafletProxy("map") %>%
    fitBounds(long_min1,latit_min1,long_max1,latit_max1)})
    
# # Add in any manually entered address
# observeEvent(input$update,{
#   # Geocode address
#   full.address <- paste(input$address)
#   geocoded.address <- geocode(full.address, source=c("dsk"), messaging=TRUE, override_limit=TRUE)
#   longitude <- geocoded.address$lon
#   latitude <- geocoded.address$lat
#   
#   # this updates the map by: 
#   leafletProxy("map") %>% 
#     addProviderTiles(providers$CartoDB.Positron) %>%
#   setView(lng=longitude, lat=latitude, zoom=15) %>%  # recentering it around the provided address and setting zoom level
#   addMarkers(lng=longitude, lat=latitude, popup=input$address) # adding a marker for the address
#     })
    
observeEvent(c(input$sour_auth, input$store_grou, input$county, input$loadstores1, input$update,input$pantry_sel),{
storepal<-colorFactor(palette="Paired",storedata$store_grou,reverse=TRUE)

 leafletProxy("map") %>%
    clearMarkers() %>%
    clearControls() %>%
    addPolygons(data=cty_boundary(),
                fillOpacity=0,
                opacity=0.7,
                stroke=TRUE,
                color="black") %>%
    addCircleMarkers(data=countydata_select(),
                opacity=0.4,
                color="#603a31",
                weight=2,
                fillOpacity=0.8,
                radius=4,
                fillColor=~storepal(store_grou),
                popup=countydata_select()$content) %>%
   addLegend(data=storedata,"topright",pal=storepal,
             values=~store_grou,title="Store category",
             opacity=1)
})

leafletOutput("map",height=900)

```

SNAP-Ed Program Locations
=====================================  

Column {.sidebar data-width=400}
-----------------------------------------------------------------------

### Data selection

This map allows you to view SNAP-Ed program locations and related services by Georgia county. Choose the name of the county in the county selection search box and then select the program(s) you want. Then click on the load data button. See the "About this map" tab for more information.

Click on a point to see more information on that site.

```{r input_2}
selectInput("county1","County selection",
            choices=gacounties$fullname,
            selected="Fulton County, GA")

checkboxGroupInput("officegroup", 
                    ("Programs"), 
                    choices = list("UGA Extension" = "UGA Extension", 
                                   "DFCS" = "DFCS", 
                                   "County Health Office" = "County Health Office",
                                   "UGA SNAP-Ed" = "UGA SNAP-Ed",
                                   "Open Hand Atlanta" = "Open Hand Atlanta",
                                   "HealthMPowers" = "HealthMPowers",
                                   "Dept of Public Health" = "Dept of Public Health"),
                              selected = c("UGA Extension","DFCS", "County Health Office", "UGA SNAP-Ed", "Open Hand Atlanta", "HealthMPowers", "Dept of Public Health"))

HTML("If no offices are visible, click on the button below")

actionButton("loadstores2","Load locations")

HTML("<br>Download a spreadsheet of selected offices<br>")

downloadButton('downloadData','Download Result Set')

downloadHandler(filename = function() {
     paste("SNAPoffices_",input$county1,"_",Sys.Date(),".csv",sep="")
   },
     content = function(file) {
     write.csv(county1data_select(), file, row.names = FALSE)
   }
)

HTML("<br>Data source: USDA Benefits Redemption Division<br>")


```

Column {data-height=600}
-----------------------------------------------------------------------

```{r program_sites}
#Load store boundaries
cty_boundary3<-reactive({
  st_fips<-as.character(gacounties %>%
    dplyr::filter(fullname==input$county1) %>%
    mutate(fips=paste("G",stcty_fips,sep="")) %>%
    select(fips))
  
  cty_fips<-gacounties %>%
    filter(fullname==input$county1) %>%
    mutate(cty_fips_sel=paste("G",stcty_fips,sep=""),
           st_fips=paste("G",st_fips,sep="")) %>%
    select(cty_fips_sel,st_fips)
  st_fips<-cty_fips$st_fips
  cty_select<-st_read("data/uscounties_st.gpkg",layer=st_fips) %>%
    filter(CTY_TXT==cty_fips$cty_fips_sel)
  # cty_boundary2<-as_Spatial(cty_select)
  # spTransform(cty_boundary2, CRS("+init=epsg:4326"))
  # cty_boundary2<-st_transform(cty_select,4326)
})

#Eligibility map
eligibility<-st_read("data/eligible_area_2017_2018.geojson",quiet=TRUE)
#   
#Load store data from county selection
programloc<-st_read("data/programloc_200321.gpkg",layer="programloc_200321",stringsAsFactors=FALSE,quiet=TRUE)

county1data_reactive<-reactive({
  fips<-as.character(gacounties %>%
    dplyr::filter(fullname==input$county1) %>%
    mutate(fips=paste("G",stcty_fips,sep="")) %>%
    select(fips))

  data<-programloc %>%
    filter(GEOID==substr(fips,2,6)) %>%
    mutate(lat=X,long=Y,
      #Define the popup
      addr_full=if_else(is.na(Zip),
                         paste("<br>",addresses),
                         paste("<br>",addresses," ",Zip,sep="")),
      content=paste("<b>Program category: </b>",Type,
                    "<br><b>Program name: </b><size=1>",Name,"</size>", 
                    "<br><b>Program location: </b>",addr_full
                    ))
  
  })

#Subset data based on store type
county1data_select<-reactive({
  county1data_reactive() %>%
    filter(Type %in% input$officegroup)
})

# observeEvent
# county1data_df<-reactive({
#   county1data_select()
  # st_set_geometry(NULL) %>%
  #   select(-lat,-long,-addr_full,-content)
# })

#Create a map  
  buffer<-0.02

output$map1<-renderLeaflet({
  long_max3<-as.vector(st_bbox(cty_boundary3()))[3]+buffer
  latit_max3<-as.vector(st_bbox(cty_boundary3()))[4]+buffer
  long_min3<-as.vector(st_bbox(cty_boundary3()))[1]-buffer
  latit_min3<-as.vector(st_bbox(cty_boundary3()))[2]-buffer

  leaflet(cty_boundary3()) %>%
  fitBounds(long_min3,latit_min3,long_max3,latit_max3) %>%
       addProviderTiles(providers$CartoDB.Positron) %>%
       addPolygons(data = eligibility,
                   stroke = FALSE, fillColor = "grey",
                   fillOpacity = 0.3, smoothFactor = 2, group = "SNAP-Ed eligible area") %>%
       addLayersControl(
         overlayGroups = c("SNAP-Ed eligible area"),
         options = layersControlOptions(collapsed = FALSE)
       )
})

# observeEvent(input$county1,{
#   long_max2<-as.vector(st_bbox(cty_boundary2()))[3]+buffer
#   latit_max2<-as.vector(st_bbox(cty_boundary2()))[4]+buffer
#   long_min2<-as.vector(st_bbox(cty_boundary2()))[1]+buffer
#   latit_min2<-as.vector(st_bbox(cty_boundary2()))[2]+buffer
# 
#   leafletProxy("map1") %>%
#     fitBounds(long_min2,latit_min2,long_max2,latit_max2)})

observeEvent(c(input$officegroup, input$county1, input$loadstores2),{
 #storepal<-colorFactor(palette="YlOrRd",msadata_reactive()$year_range,reverse=TRUE)
  # storepal<-colorFactor(palette="Dark2",county1data_reactive()$Type,reverse=TRUE)
  #storepal1<-colorFactor(topo.colors(7), county1data_reactive()$Type)
  storepal1<-colorFactor(palette= c("greenyellow","limegreen","turquoise1","dodgerblue2","goldenrod1","brown2","mediumpurple1"),unique(programloc$Type),reverse=TRUE)

  long_max4<-as.vector(st_bbox(cty_boundary3()))[3]+buffer
  latit_max4<-as.vector(st_bbox(cty_boundary3()))[4]+buffer
  long_min4<-as.vector(st_bbox(cty_boundary3()))[1]+buffer
  latit_min4<-as.vector(st_bbox(cty_boundary3()))[2]+buffer
  
 leafletProxy("map1") %>%
    clearMarkers() %>%
    clearControls() %>%
    addPolygons(data=cty_boundary3(),
                fillOpacity=0,
                opacity=0.7,
                stroke=TRUE,
                color="black") %>%
    addCircleMarkers(data=county1data_select(),
               opacity=0.4,
               color="#603a31",
               weight=2,
               fillOpacity=0.8,
               radius=4,
               fillColor=~storepal1(Type),
               popup=county1data_select()$content) %>%
   addLegend(data=county1data_reactive(),"topright",pal=storepal1,
             values=~Type,title="Site category",
             opacity=1)
})

leafletOutput("map1",height=900)

```

About this map
=====================================  

1. SNAP-Ed Food Resources
This map allows users to exlore the database of SNAP authorized retailers in 2018 in 159 counties in GA. Users can compare their locations to the WIC authorized retailers by using the "Source" check box in the sidebar. Also, SNAP exclusive/WIC exclusive/both SNAP & WIC authorized details are addressed in the pop-up box when users click on a point. 

    <strong>SNAP authorized retailers are classified as follows (Store category): Farmers Market/Grocer/Local Foods/Small retail/Specialty/Supermarket/Other store.<br>
    There is no specific category for WIC authorized retailers.</strong>



2. SNAP-Ed Program Locations
This map includes SNAP office locations and also SNAP implementation sites.

    <strong>-SNAP office locations: DFCS Office/UGA Extension Office/County Health Office<br> 
    -SNAP implementation sites:UGA ("UGA Site Loc" in the category)/Open Hand Atlanta/HealthMPowers/DPH (Department of Public Health)</strong>
  

