---
title: "SNAP-Ed Resources"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(leaflet)
library(sf)
library(shinyWidgets)
library(rgdal)
library(ggmap)

gacounties<-read_csv("data/county_list.csv") %>%
  arrange(fullname)

years<-c(2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018)

```

SNAP-Ed Food Resources
=====================================  

Column {.sidebar data-width=400}
-----------------------------------------------------------------------

### Data selection

This map allows you to view SNAP and WIC authorized retailers in Georgia by. Choose the name of the county in the county selection search box and then select the relevant program. Click on a point to see more information on that retailer.

```{r}
selectInput("county","County selection",
            choices=gacounties$fullname)

textInput(inputId = "address", label = "Enter address:", 
            value="", placeholder = "e.g. 210 Field St., Athens, GA, 30602")
actionButton("update" , label = HTML("Update map and center<br />around provided address"), icon("refresh"), class = "btn btn-primary")

# pickerInput(
#   inputId = "years2", 
#   label = "Select the year(s) retailers were SNAP authorized", 
#   choices = years, 
#   selected=max(years),
#   options = list(
#     `actions-box` = TRUE, 
#     size = 10,
#     `selected-text-format` = "count > 4"
#   ), 
#   multiple = TRUE
# )

checkboxGroupInput("auth_program", 
                    ("Source"), 
                    choices = list("SNAP" = "SNAP", 
                                   "WIC" = "WIC"),
                              selected = c("SNAP","WIC"))

HTML("If no stores are visible, click on the button below")

actionButton("loadstores1","Load stores")

HTML("<br>Download a spreadsheet of selected retailers<br>")

downloadButton('downloadData','Download Result Set')

downloadHandler(filename = function() {
     paste("SNAPretailers_",input$county,"_",Sys.Date(),".csv",sep="")
   },
     content = function(file) {
     write.csv(countydata_df(), file, row.names = FALSE)
   }
)

HTML("<br>Data source: USDA Benefits Redemption Division<br>")


```

Column {data-height=600}
-----------------------------------------------------------------------

```{r}
#Load county boundary
cty_boundary<-reactive({
  st_fips<-as.character(gacounties %>%
    dplyr::filter(fullname==input$county) %>%
    mutate(fips=paste("G",stcty_fips,sep="")) %>%
    select(fips))
  
  cty_fips<-gacounties %>%
    filter(fullname==input$county) %>%
    mutate(cty_fips_sel=paste("G",stcty_fips,sep=""),
           st_fips=paste("G",st_fips,sep="")) %>%
    select(cty_fips_sel,st_fips)
  st_fips<-cty_fips$st_fips
  cty_select<-st_read("data/uscounties_st.gpkg",layer=st_fips) %>%
    filter(CTY_TXT==cty_fips$cty_fips_sel)
  cty_boundary1<-as_Spatial(cty_select)
  spTransform(cty_boundary1, CRS("+init=epsg:4326"))
})

#Load ga_retailers
retailersdata<-reactive({
    data<-read_csv("data/program_retail_ga.csv") %>%
      st_as_sf(coords=c("X","Y"),crs=4326)
  })

#Load store data from county selection
countydata_reactive<-reactive({
  data<-read_csv("data/program_retail_ga.csv") %>%
    st_as_sf(coords=c("X","Y"),crs=4326,remove=FALSE) %>%
    mutate(lat=X,long=Y,
      #Define the popup
      addr_full=if_else(is.na(addr_add),
                         paste("<br><b>",addr_num," ",addr_st," ",sep=""),
                         paste("<br><b>",addr_num," ",addr_st," ",addr_add,sep="")),
      # year_range=case_when(year_first==year_last~as.character(year_first),
      #                      year_first!=year_last~paste(year_first,year_last,sep="-")),
      content=paste("<strong><size=1>",store_name,"</strong></size>", 
                       addr_full,
                       "<br>",city,", ",state,"  ",zip5,"</b>",
                       "<br><br><b>USDA store classification:</b> ",store_type,
                       "<br><b>Group category: </b>",store_grou,
                       "<br><b>Authorization: </b>",program,
                       # "<br><b>Years authorized for SNAP*: </b>",year_range,
                       "<br>*2018 year data are available.",sep="")) %>%
    filter(Source %in% input$auth_program)
  })

# observeEvent
countydata_df<-reactive({
  countydata_reactive() %>%
  st_set_geometry(NULL) %>%
    select(-lat,-long,-addr_full,-content)
})

#Create a map  
  buffer<-0.02

output$map<-renderLeaflet({
  long_max<-as.vector(st_bbox(cty_boundary()))[3]+buffer
  latit_max<-as.vector(st_bbox(cty_boundary()))[4]+buffer
  long_min<-as.vector(st_bbox(cty_boundary()))[1]-buffer
  latit_min<-as.vector(st_bbox(cty_boundary()))[2]-buffer

  leaflet(countydata_reactive()) %>%
  fitBounds(long_min,latit_min,long_max,latit_max) %>%
  addTiles() 
})

observeEvent(input$county,{
  long_max1<-as.vector(st_bbox(cty_boundary()))[3]+buffer
  latit_max1<-as.vector(st_bbox(cty_boundary()))[4]+buffer
  long_min1<-as.vector(st_bbox(cty_boundary()))[1]-buffer
  latit_min1<-as.vector(st_bbox(cty_boundary()))[2]-buffer
  
  leafletProxy("map") %>%
    fitBounds(long_min1,latit_min1,long_max1,latit_max1)})
    
# Add in any manually entered address
observeEvent(input$update,{
  # Geocode address
  full.address <- paste(input$address)
  geocoded.address <- geocode(full.address, source=c("dsk"), messaging=TRUE, override_limit=TRUE)
  longitude <- geocoded.address$lon
  latitude <- geocoded.address$lat
  
  # this updates the map by: 
  leafletProxy("map") %>% 
  setView(lng=longitude, lat=latitude, zoom=12) %>%  # recentering it around the provided address and setting zoom level
  addMarkers(lng=longitude, lat=latitude, popup=input$address) # adding a marker for the address
    })
    
observeEvent(c(input$Source, input$store_grou, input$county, input$loadstores1, input$update),{
 #storepal<-colorFactor(palette="YlOrRd",msadata_reactive()$year_range,reverse=TRUE)
  storepal<-colorFactor(palette="Dark2",countydata_reactive()$store_grou,reverse=TRUE)

 leafletProxy("map") %>%
    clearMarkers() %>%
    clearControls() %>%
    addPolygons(data=cty_boundary(),
                fillOpacity=0,
                opacity=0.7,
                stroke=TRUE,
                color="black") %>%
    addCircleMarkers(data=retailersdata(),
               opacity=0.4,
               color="#603a31",
               weight=2,
               fillOpacity=0.8,
               radius=4,
               fillColor=~storepal(store_grou))%>%
   addCircleMarkers(data=countydata_reactive(),
               opacity=0.4,
               color="#603a31",
               weight=2,
               fillOpacity=0.8,
               radius=4,
               fillColor=~storepal(store_grou),
               popup=countydata_reactive()$content) %>%
   addLegend(data=countydata_reactive(),"topright",pal=storepal,
             values=~store_grou,title="Store category",
             opacity=1)
})

leafletOutput("map",height=900)

```

SNAP-Ed Program Locations
=====================================  

Column {.sidebar data-width=400}
-----------------------------------------------------------------------

### Data selection

This map allows you to view SNAP-Ed program locations and related services by Georgia county. Choose the name of the county in the county selection search box and then select the program(s) you want. Then click on the load data button. See the "About this map" tab for more information.

Click on a point to see more information on that site.

```{r}
selectInput("county1","County selection",
            choices=gacounties$fullname)

checkboxGroupInput("officegroup", 
                    ("Programs"), 
                    choices = list("UGA Extension" = "UGA Extension", 
                                   "DFCS" = "DFCS", 
                                   "County Health Office" = "HealthDep",
                                   "UGA SNAP-Ed" = "UGA Site",
                                   "Open Hand Atlanta" = "Open Hand Atlanta",
                                   "HealthMPower" = "HealthMPower",
                                   "Dept. of Public Health" = "DPH"),
                              selected = c("UGA Extension","DFCS", "HealthDep", "UGA Site", "Open Hand Atlanta", "HealthMPower", "DPH"))

HTML("If no offices are visible, click on the button below")

actionButton("loadstores2","Load locations")

HTML("<br>Download a spreadsheet of selected offices<br>")

downloadButton('downloadData','Download Result Set')

downloadHandler(filename = function() {
     paste("SNAPoffices_",input$county1,"_",Sys.Date(),".csv",sep="")
   },
     content = function(file) {
     write.csv(county1data_df(), file, row.names = FALSE)
   }
)

HTML("<br>Data source: USDA Benefits Redemption Division<br>")


```

Column {data-height=600}
-----------------------------------------------------------------------

```{r}
#Load store boundaries
cty_boundary3<-reactive({
  st_fips<-as.character(gacounties %>%
    dplyr::filter(fullname==input$county1) %>%
    mutate(fips=paste("G",stcty_fips,sep="")) %>%
    select(fips))
  
  cty_fips<-gacounties %>%
    filter(fullname==input$county1) %>%
    mutate(cty_fips_sel=paste("G",stcty_fips,sep=""),
           st_fips=paste("G",st_fips,sep="")) %>%
    select(cty_fips_sel,st_fips)
  st_fips<-cty_fips$st_fips
  cty_select<-st_read("data/uscounties_st.gpkg",layer=st_fips) %>%
    filter(CTY_TXT==cty_fips$cty_fips_sel)
  cty_boundary2<-as_Spatial(cty_select)
  spTransform(cty_boundary2, CRS("+init=epsg:4326"))
})

#Load store data from county selection
county1data_reactive<-reactive({
  fips<-as.character(gacounties %>%
    dplyr::filter(fullname==input$county1) %>%
    mutate(fips=paste("G",stcty_fips,sep="")) %>%
    select(fips))

  data<-st_read("data/snap_programs_gacounties.gpkg",layer=fips,stringsAsFactors=FALSE) %>%
    mutate(lat=X,long=Y,
      #Define the popup
      addr_full=if_else(is.na(Zip),
                         paste("<br>",addresses),
                         paste("<br>",addresses," ",Zip,sep="")),
      content=paste("<size=1>",Name,"</size>", 
                       addr_full))
  })

#Subset data based on store type
county1data_select<-reactive({
  county1data_reactive() %>%
    filter(Type %in% input$officegroup)
})

# observeEvent
county1data_df<-reactive({
  county1data_select() %>%
  st_set_geometry(NULL) %>%
    select(-lat,-long,-addr_full,-content)
})

#Create a map  
  buffer<-0.02

output$map1<-renderLeaflet({
  long_max3<-as.vector(st_bbox(cty_boundary3()))[3]+buffer
  latit_max3<-as.vector(st_bbox(cty_boundary3()))[4]+buffer
  long_min3<-as.vector(st_bbox(cty_boundary3()))[1]-buffer
  latit_min3<-as.vector(st_bbox(cty_boundary3()))[2]-buffer

  leaflet(cty_boundary3()) %>%
  fitBounds(long_min3,latit_min3,long_max3,latit_max3) %>%
   addProviderTiles(providers$CartoDB.Positron)
})

# observeEvent(input$county1,{
#   long_max2<-as.vector(st_bbox(cty_boundary2()))[3]+buffer
#   latit_max2<-as.vector(st_bbox(cty_boundary2()))[4]+buffer
#   long_min2<-as.vector(st_bbox(cty_boundary2()))[1]+buffer
#   latit_min2<-as.vector(st_bbox(cty_boundary2()))[2]+buffer
# 
#   leafletProxy("map1") %>%
#     fitBounds(long_min2,latit_min2,long_max2,latit_max2)})

observeEvent(c(input$officegroup, input$county1, input$loadstores2),{
 #storepal<-colorFactor(palette="YlOrRd",msadata_reactive()$year_range,reverse=TRUE)
  storepal<-colorFactor(palette="Dark2",county1data_reactive()$Type,reverse=TRUE)

  long_max4<-as.vector(st_bbox(cty_boundary3()))[3]+buffer
  latit_max4<-as.vector(st_bbox(cty_boundary3()))[4]+buffer
  long_min4<-as.vector(st_bbox(cty_boundary3()))[1]+buffer
  latit_min4<-as.vector(st_bbox(cty_boundary3()))[2]+buffer
  
 leafletProxy("map1") %>%
    clearMarkers() %>%
    clearControls() %>%
    addPolygons(data=cty_boundary3(),
                fillOpacity=0,
                opacity=0.7,
                stroke=TRUE,
                color="black") %>%
    addCircleMarkers(data=county1data_select(),
               opacity=0.4,
               color="#603a31",
               weight=2,
               fillOpacity=0.8,
               radius=4,
               fillColor=~storepal(Type),
               popup=county1data_select()$content) %>%
   addLegend(data=county1data_reactive(),"topright",pal=storepal,
             values=~Type,title="Site category",
             opacity=1)
})

leafletOutput("map1",height=900)

```

About this map
=====================================  

1. SNAP-Ed Food Resources
This map allows users to exlore the database of SNAP authorized retailers in 2018 in 159 counties in GA. Users can compare their locations to the WIC authorized retailers by using the "Source" check box in the sidebar. Also, SNAP exclusive/WIC exclusive/both SNAP & WIC authorized details are addressed in the pop-up box when users click on a point. 

    <strong>SNAP authorized retailers are classified as follows (Store category): Farmers Market/Grocer/Local Foods/Small retail/Specialty/Supermarket/Other store.<br>
    There is no specific category for WIC authorized retailers.</strong>



2. SNAP-Ed Program Locations
This map includes SNAP office locations and also SNAP implementation sites.

    <strong>-SNAP office locations: DFCS Office/UGA Extension Office/County Health Office<br> 
    -SNAP implementation sites:UGA ("UGA Site Loc" in the category)/Open Hand Atlanta/HealthMPowers/DPH (Department of Public Health)</strong>
  

